Control-Flow Integrity Checking

### 2012-01-26 slides/slides.tex
Add some listings from the paper.

\documentclass[serif,slidestop,compress,red]{beamer}
%\usepackage[utf8]{inputenc}

@@

\usepackage{fontspec}
%\fontspec{Ubuntu}
%\fontspec{Helsinki}
%\fontspec{Vollkorn}
\usepackage{xltxtra}
\setmainfont{Ubuntu}
\setmonofont{Courier 10 Pitch}
%\setromanfont{Helsinki}

@@

\title{Compiler-Unterstützung für \\ Control-Flow Integrity Checking}
\subtitle{Vortrag im Hauptseminar Betriebssysteme}
\author{Hermann Loose}

@@

@@

>>>>

\documentclass[serif,slidestop,compress,red]{beamer}
%\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage{listings}

@@

\usepackage{fontspec}
%\fontspec{Ubuntu}
%\fontspec{Helsinki}
%\fontspec{Vollkorn}
\usepackage{xltxtra}
\setmainfont{Ubuntu}
\setmonofont{Courier 10 Pitch}
\setromanfont{Ubuntu}
\setsansfont{Ubuntu}

@@

\title{Control-Flow Integrity Checking}
\subtitle{Vortrag im Hauptseminar Betriebssysteme}
\author{Hermann Loose}

\definecolor{light-gray}{gray}{0.7}

\DeclareCaptionFont{white}{\color{white}}
\DeclareCaptionFormat{listing}{\colorbox{gray}{\parbox{\textwidth}{\hspace{0.9em}#1#2#3}}}
\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white,font={sf}}

@@

\definecolor{keywords}{RGB}{255,0,90}
\definecolor{comments}{RGB}{100,100,100}
\lstset{
  language=[x86masm]Assembler,
  basicstyle=\ttfamily
  %frame=lines
}

@@

\begin{frame}[fragile]
  \frametitle{Ausgangspunkt}
  \begin{lstlisting}[title=Quelle]

  jmp ecx              ; computed jump
  \end{lstlisting}
  \begin{lstlisting}[title=Ziel]

  mov eax, [esp+4]     ; dst
  \end{lstlisting}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Instrumentierung — Variante 1}
  \begin{lstlisting}[title=Quelle]
  cmp [ecx], 12345678h ; comp ID & dst
  jne error_label      ; if != fail
  lea ecx, [ecx+4]     ; skip ID at dst
  jmp ecx              ; jump to dst
  \end{lstlisting}
  \begin{lstlisting}[title=Ziel]
  ; data 12345678h     ; ID
  mov eax, [esp+4]     ; dst
  \end{lstlisting}
\end{frame}

%\begin{frame}[fragile]
%  \frametitle{Quelle — erster Versuch}
%  \begin{lstlisting}
%  cmp [ecx], 12345678h ; 81 39 78 56 34 12
%  jne error_label      ; 75 13
%  lea ecx, [ecx+4]     ; 8D 49 04
%  jmp ecx              ; FF E1
%  \end{lstlisting}
%\end{frame}

\begin{frame}[fragile]
  \frametitle{Instrumentierung — Variante 1}
  \begin{lstlisting}[title=Quelle,escapechar=!]
  cmp [ecx], !\colorbox{light-gray}{12345678h}! ; 81 39 !\emph{\colorbox{light-gray}{78 56 34 12}}!
  jne error_label      ; 75 13
  lea ecx, [ecx+4]     ; 8D 49 04
  jmp ecx              ; FF E1
  \end{lstlisting}
  \textbf{Problem:} die ID ist in die \texttt{cmp} Instruktion eingebettet, \\ macht
  damit \texttt{jne error\_label} zu einem gültigen Ziel
\end{frame}

\begin{frame}[fragile]
  \frametitle{Instrumentierung — Variante 2}
  \begin{lstlisting}[title=Quelle]
  mov eax, 12345677h ; load ID-1
  inc eac            ; increment ID
  cmp [ecx+4], eax   ; compare w/ dst
  jne error_label    ; if != fail
  jmp ecx            ; jump to label
  \end{lstlisting}
  \begin{lstlisting}[title=Ziel]
  prefetchnta        ; label
     [12345678h]     ;    ID
  mov eax, [esp+4]   ; dst
  \end{lstlisting}
\end{frame}
